---
title: "Linear Regression"
author: "Yichang Liu 501777"
date: "1/3/2022"
output: pdf_document
---

\section{Linear Regression}
```{r}
library(MASS)
attach(Boston)
names(Boston)
```
\subsection{Main Part of Linear Regression}
```{r}
lm.fit=lm(medv~lstat, data = Boston)
names(lm.fit)
summary(lm.fit) ### more information
```

Least Square Method: $MSE = \frac{1}{n}\sum^{n}_{i=1}(Y_i-\hat{Y}_i)^2 = \frac{1}{n}\sum^{n}_{i=1}(Y_i-\hat{\beta_0} - \hat{\beta_1}X_1, ....,\hat{\beta_p}X_p)^2$. 

\subsection{Coefficient}
Use the elements in the names(lm.fit)
```{r}
lm.fit$coefficients  ### the first method
coef(lm.fit)         ### the second method
```

\subsection{Confidence Interval and Prediction Interval}
```{r}
confint(lm.fit)      ### confidence interval for Betas
```

\textbf{Predict using predict():}

Prediction intervals must account for both the uncertainty in estimating the population mean, plus the random variation of the individual values. So a prediction interval is always wider than a confidence interval. The prediction interval will not converge to a single value as the sample size increases.

\textbf{Prediction interval:}
```{r}
predict(lm.fit, data.frame(lstat=c(5,10,15)), interval="confidence")
predict(lm.fit,data.frame(lstat=c(5,10,15)),interval="prediction")
```