---
title: "Logistic Regression"
author: "Yichang Liu 501777"
date: "1/10/2022"
output: pdf_document
---
```{r}
library(ISLR)
attach(Smarket)
```

\subsection{Logistic Regression}
\subsection{Logistic Regression WITHOUT TRAINING DATA}
glm() needs to add "family = binomial". 
```{r}
glm.fit = glm(Direction~Lag1+Lag2+Lag3+Lag4+Lag5+Volume, data = Smarket, family = binomial)
names(glm.fit)
summary(glm.fit)
```

```{r}
coef(glm.fit) ### coef() to get all the coefficient of the model
```
```{r}
summary(glm.fit)$coef
```

```{r}
glm.probs = predict(glm.fit, type = "response")
glm.probs[1:10]
```

```{r}
glm.pred = rep("Down",length(glm.probs))
glm.pred[glm.probs>0.5]="Up"
glm.pred[1:10]
```

```{r}
table(glm.pred,Direction)
mean(glm.pred == Direction)
```

\subsection{Logistic Regression WITH TRAINING DATA}

Firstly, define the test data(also can define the training data)
```{r}
train = (Year<2005)
Smarket.2005 = Smarket[!train,]
dim(Smarket.2005)
Direction.2005 = Direction[!train]
```
glm.fit use the training data

predict() -- get the prediction of test data by using the model constructed by training data. ADD "type = "response"
```{r}
glm.fit = glm(Direction~Lag1+Lag2+Lag3+Lag4+Lag5+Volume, 
              data = Smarket,
              family = binomial, 
              subset = train)
glm.probs = predict(glm.fit,Smarket.2005,type = "response")
head(glm.probs)
```
be able to use str() to get the quantitive value of dummy variable. 

```{r}
glm.pred = rep("Down", length(glm.probs))
glm.pred[glm.probs>.5] = "Up"
table(glm.pred,Direction.2005)
mean(glm.pred == Direction.2005)
mean(glm.pred != Direction.2005)  ### error rate
```

\subsubsection{logistic regression to some specific points}
```{r}
glm.fit = glm(Direction ~ Lag1+Lag2, data = Smarket, family = binomial, subset = train)
glm.probs = predict(glm.fit,Smarket.2005, type = "response")
glm.pred = rep("Down", length(glm.probs))
glm.pred[glm.probs>0.5] = "Up"
table(glm.pred,Direction.2005)
mean(glm.pred == Direction.2005)
predict(glm.fit,newdata = data.frame(Lag1 = c(1.2,1.5),Lag2 = c(1.1,-0.8)),type="response")
```